Atomify - a live LAMMPS visualizer

### 2017-06-16 ms.tex
Restructure implementation intro

Atomify runs a LAMMPS instance in the background that the user can issue 
commands to and visualizes the current atom positions and the LAMMPS state.
The user can interact with LAMMPS while the simulation is running.
Atomify is written in C++ and QML using the Qt framework.
The GUI is developed in QML and LAMMPS communication,
computations, and rendering is mostly defined in C++.
High-performance visualization is implemented as billboards in Qt3D.

>>>>

Atomify runs a LAMMPS instance in the background that it issues commands to.
The current state and atom positions are extracted from this instance for
visualization.
This setup makes it possible for the user to interact with LAMMPS while the
simulation is running.
Atomify is written in C++ and QML using the Qt framework.
The GUI is written in QML, while LAMMPS communication,
computations, and rendering is written in C++.
High-performance visualization is implemented as billboards in Qt3D.
